Social Housing in Toronto

### 2024-04-22 paper/paper.qmd
commit

# Data {#sec-data}

Data Sourcing

@@

Data Cleaning

@@

# Create a plot
ggplot(plot_data, 
       aes(x = quarter_year)) +
  geom_point(aes(y = test), color = "red") +
  geom_point(aes(y = housed), color = "blue") +
  scale_color_manual(values = c("blue", "red")) +
  labs(title = "Yearly New/Reactivated Applications vs. Housed",
       x = "Year Quarter",
       y = "Application Status") +
  theme_minimal() +
  theme(legend.title = element_blank())

@@

# Create a data frame
plot_data <- data.frame(
              quarter_year = year_quarter,
              test = total_active_waiting_list,
              seniors = seniors
            )

@@

# Create a plot
ggplot(plot_data, aes(x = quarter_year)) +
  geom_point(aes(y = test), color = "red") +
  geom_point(aes(y = housed), color = "blue") +
  scale_color_manual(values = c("blue", "red")) +
  labs(title = "Total Active Applications vs. Seniors' Applications",
       x = "Quarter Year",
       y = "Application Numbers") +
  theme_minimal() +
  theme(legend.title = element_blank())

@@

# Extract relevant columns with adjusted column names
year_quarter <- analysis_data$Quarter_Year
tes1 <- analysis_data$Household_no_dependents
test2 <- analysis_data$Household_with_dependents

# Create a data frame
plot_data <- data.frame(Year_Quarter = year_quarter,
                        test1 = household_no_dependents,
                        test2 = household_with_dependents)

# Convert Year_Quarter to factor to maintain order
plot_data$Year_Quarter <- factor(plot_data$Year_Quarter, levels = unique(plot_data$Year_Quarter))

# Create a line plot
ggplot(plot_data, aes(x = Year_Quarter)) +
  geom_point(aes(y = household_no_dependents, color = "red")) +
  geom_point(aes(y = household_with_dependents, color = "blue")) +
  scale_color_manual(values = c("blue", "red")) +
  labs(title = "Households with and without Dependents Applying for Social Housing",
       x = "Year Quarter",
       y = "Application Numbers") +
  theme_minimal() +
  theme(legend.title = element_blank())

@@

The line plot @figure4 comparing households with and without dependents applying for social housing from Q1 2019 to Q4 2023 provides valuable insights into the composition of applicants and potential variations in housing needs among different household types over time. From the graph, we observe fluctuations in both the number of households with and without dependents applying for social housing throughout the observed period. Interestingly, the number of households with dependents appears to fluctuate more prominently compared to households without dependents, as indicated by the greater variability in the dashed line representing households with dependents.

@@

# Create a line plot
ggplot(plot_data, aes(x = quarter_year)) +
  geom_point(aes(y = Inactive_Cancelled, color = "Inactive/Cancelled")) +
  geom_point(aes(y = Total_Active_Waiting_List, color = "Total Active Waiting List")) +
  scale_color_manual(values = c("blue", "red")) +
  labs(title = "Inactive/Cancelled vs Total Active Waiting List",
       x = "Quarter Year",
       y = "Application Status") +
  theme_minimal() +
  theme(legend.title = element_blank())

@@

# Additional data details

>>>>

# Data Sourcing

@@

#Data Cleaning

@@

# Create a dot plot
ggplot(plot_data, 
       aes(x = quarter_year)) +
  geom_point(aes(y = test), color = "red") +
  geom_point(aes(y = housed), color = "blue") +
  scale_color_manual(values = c("blue", "red")) +
  labs(title = "Yearly New/Reactivated Applications vs. Housed",
       x = "Year Quarter",
       y = "Application Status") +
  theme_minimal() +
  theme(legend.title = element_blank())

@@

# Create a data frame
plot_data <- data.frame(
              quarter_year = year_quarter,
              test = test,
              seniors = seniors
            )

@@

# Create a dot plot
ggplot(plot_data, aes(x = quarter_year)) +
  geom_point(aes(y = test), color = "red") +
  geom_point(aes(y = housed), color = "blue") +
  scale_color_manual(values = c("blue", "red")) +
  labs(title = "Total Active Applications vs. Seniors' Applications",
       x = "Quarter Year",
       y = "Application Numbers") +
  theme_minimal() +
  theme(legend.title = element_blank())

@@

# Extract relevant columns with adjusted column names
year_quarter <- analysis_data$quarter_year
test1 <- analysis_data$household_no_dependents
test2 <- analysis_data$household_with_dependents

# Create a data frame
plot_data <- data.frame(Year_Quarter = year_quarter,
                        test1 = test1,
                        test2 = test2)

# Create a line plot
ggplot(plot_data, aes(x = Year_Quarter)) +
  geom_point(aes(y = test1, color = "red",group = 1)) +
  geom_point(aes(y = test2, color = "blue",group = 2)) +
  scale_color_manual(values = c("blue", "red")) +
  labs(title = "Households with and without Dependents Applying for Social Housing",
       x = "Year Quarter",
       y = "Application Numbers") +
  theme_minimal()

@@

The dot plot @figure4 comparing households with and without dependents applying for social housing from Q1 2019 to Q4 2023 provides valuable insights into the composition of applicants and potential variations in housing needs among different household types over time. From the graph, we observe fluctuations in both the number of households with and without dependents applying for social housing throughout the observed period. Interestingly, the number of households with dependents appears to fluctuate more prominently compared to households without dependents, as indicated by the greater variability in the dashed line representing households with dependents.

@@

# Create a dot plot
ggplot(plot_data, aes(x = quarter_year)) +
  geom_point(aes(y = Inactive_Cancelled, color = "Inactive/Cancelled")) +
  geom_point(aes(y = Total_Active_Waiting_List, color = "Total Active Waiting List")) +
  scale_color_manual(values = c("blue", "red")) +
  labs(title = "Inactive/Cancelled vs Total Active Waiting List",
       x = "Quarter Year",
       y = "Application Status") +
  theme_minimal() +
  theme(legend.title = element_blank())

@@
